Red, Blue, or Purple? 2024’s Battleground States Tell a Story

### 2024-11-04 paper/paper.qmd
table formatting done

According to @tbl-outcome_variables, the outcome variables include critical components for analyzing polling data, such as State, Pollster, Pollscore, Candidate Name, Percentage (pct), Sample Size, Start Date, End Date, and Days to Election. These variables provide the foundation for estimating actual vote shares by capturing regional differences, pollster credibility, candidate-specific support, and timing in relation to Election Day. Together, they ensure a nuanced approach to election forecasting that accounts for variability in poll methodology and voter sentiment shifts over time.
```{r}
#| label: tbl-outcome_variables
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

# Create the table with an Example column
outcome_variables %>%
  kable(
    col.names = c("Outcome Variable", "Example"),
    caption = "Outcome Variables",
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))
```

@@

```{r}
#| label: tbl-predictor_variables
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

# Create the table
predictor_variables %>%
  kable(
    col.names = c("Predictor Variable", "Example"),
    caption = "Predictor Variables",
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped", "scale_down", "hold_position"))
```

@@

# Display the results in a kable table with kableExtra styling
results %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "center", font_size = 14)

>>>>

According to @tbl-outcome_variables, the outcome variables include critical components for analyzing polling data, such as State, Pollster, Pollscore, Candidate Name, Percentage (pct), Sample Size, Start Date, End Date, and Days to Election. These variables provide the foundation for estimating actual vote shares by capturing regional differences, pollster credibility, candidate-specific support, and timing in relation to Election Day. Together, they ensure a nuanced approach to election forecasting that accounts for variability in poll methodology and voter sentiment shifts over time.

```{r}
#| label: tbl-outcome_variables
#| tbl-cap: "Outcome Variables"
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

# Create the table with an Example column
outcome_variables %>%
  kable(
    col.names = c("Outcome Variable", "Example"),
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped"))
```

@@

```{r}
#| label: tbl-predictor_variables
#| tbl-cap: "Predictor Variables"
#| echo: false
#| eval: true
#| warning: false
#| message: false

@@

# Create the table
predictor_variables %>%
  kable(
    col.names = c("Predictor Variable", "Example"),
    booktabs = TRUE
  ) %>%
  kable_styling(latex_options = c("striped"))
```

@@

# Display the results in a kable table with kableExtra styling
results %>%
  kable() %>%
  kable_styling(full_width = FALSE, position = "center", latex_options = c("striped"))
